A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by a pile of money from a funding agency.}

### 2017-02-16 paper/paper.tex
Words

\paragraph{Efficient representation of label classes} The algorithm as
described so far requires $\BigO{n^2}$ space at each level of the search tree,
since labels may be up to $g$ bits in length. We can reduce the memory
requirement to $\BigO{n}$ per level by storing a \emph{label class} as a pair
$\langle P,T \rangle$ for each label $l$ that is used, where $P$ is the set of
vertices in $\V(G)$ labelled $l$, and $T$ is the set of vertices in $\V(H)$
labelled $l$\footnote{We adopt terminology from subgraph isomorphism, where one
graph is a pattern graph $P$ and the other the target graph $T$.}. Since there
are $g + h$ vertices in the two graphs, at most $g + h$ label classes
can exist at once, and there are at most $g + h$ vertices in the union of
all of the $P$ and $T$ sets.  We can gain further efficiency by discarding
during search any label class that has an empty $P$ or $T$ set.

>>>>

\paragraph{Efficient representation of label classes} The algorithm as
described so far apparently requires $\BigO{n^2}$ space at each level of the
search tree.  We can reduce the memory requirement to $\BigO{n}$ per level by
storing a \emph{label class} as a pair $\langle P,T \rangle$ for each label $l$
that is used, where $P$ is the set of vertices in $\V(G)$ labelled $l$, and $T$
is the set of vertices in $\V(H)$ labelled $l$\footnote{We adopt terminology
from subgraph isomorphism, where one graph is a pattern graph $P$ and the other
the target graph $T$.}. Since there are $g + h$ vertices in the two graphs, at
most $g + h$ label classes can exist at once, and there are at most $g + h$
vertices in the union of all of the $P$ and $T$ sets.  We can gain further
efficiency by discarding during search any label class that has an empty $P$ or
$T$ set.
